Tabular Constraint Learning

### 2016-04-15 Paper/ECAI/tabular.tex
Table WIP

\sergey{Table should take into account our new notation and balance between formality and intuition, heh}
\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{l X X}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    \ecalldiff{v_x} & $\integer(v_x)$ or $\textual(v_x)$ & All elements in $v_x$ are different \\
    %X = Y & & \\
    \ecfkey{v_{fk}}{v_{pk}} & $\ptype(v_{fk})$ = $ptype(v_{pk})$,$\ptable(v_{fk}) \neq \ptable(v_{pk})$, $\ecalldiff{v_{pk}}$ & Every value in @fk also exist in @pk \\
    % TODO check out
    \eclookupprod{v_r}{v_1}{v_{fk}}{v_{pk}}{v_{val}}
      & the variables in $\{@r, @1, @fk\}$ and in $\{@pk, @val\}$ all have the same \plength, \ptable and \por.
      & $@r$ is the obtained by multiplying $@1$ with $\eclookup{@fk}{@pk}{@val}$  
      \\
    \eclookup{v_r}{v_{fk}}{v_{pk}}{v_{val}}
      & the variables in $\{@fk, @r\}$ and in $\{@pk, @val\}$ all have the same \plength, \ptable and \por; $@r$ and~$@val$ have the same type; and \ecfkey{@fk}{@pk}.
      & Lookup $@fk$ in $@pk$ and return the corresponding value in $@val$.
      \\
    \eclookupfuzzy{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecperm{v_x} & & \\
    \ecprod{v_r}{v_1}{v_2} & & \\
    \ecproj{v_r}{\mathbf{v_x}} & & \\
    \ecrank{v_r}{v_x} & Y and X have the same length & Y is the rank of X (including ties)\\
    \ectotal{v_r}{v_{pos}}{v_{neg}} & A, P and N have the same length and their length is at least 2 & *\\
    \ecseries{v_x} & & \\
    \ecsumc{v_r}{\mathbf{v_x}} & & Y is the result of summing each column in X \\
    \ecsumr{v_r}{\mathbf{v_x}} & & Y is the result of summing each row in X \\
    \ecsumif{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecsumprod{v_r}{v_1}{v_2} & & \\

>>>>

\sergey{Table should take into account our new notation and balance between formality and intuition, heh}
\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{l X X}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    \ecalldiff{v_x} & $\integer(v_x)$ or $\textual(v_x)$ & All elements in $v_x$ are different \\
    %X = Y & & \\
    \ecfkey{v_{fk}}{v_{pk}} & $\ptype(v_{fk})$ = $ptype(v_{pk})$,$\ptable(v_{fk}) \neq \ptable(v_{pk})$, $\ecalldiff{v_{pk}}$ & Every value in @fk also exist in @pk \\
    % TODO check out
    \eclookupprod{v_r}{v_1}{v_{fk}}{v_{pk}}{v_{val}}
      & the variables in $\{@r, @1, @fk\}$ and in $\{@pk, @val\}$ all have the same \plength, \ptable and \por.
      & $@r$ is the obtained by multiplying $@1$ with $\eclookup{@fk}{@pk}{@val}$.
      \\
    \eclookup{v_r}{v_{fk}}{v_{pk}}{v_{val}}
      & the variables in $\{@fk, @r\}$ and in $\{@pk, @val\}$ all have the same \plength, \ptable and \por; $@r$ and~$@val$ have the same type; and \ecfkey{@fk}{@pk}.
      & Lookup $@fk$ in $@pk$ and return the corresponding value in $@val$.
      \\
    \eclookupfuzzy{v_r}{v_{fk}}{v_{pk}}{v_{val}}
      & \textit{Same as lookup}
      & Lookup the first item in $@pk$ smaller than $@fk$ and return the corresponding value in $@val$.
      \\
    \ecperm{v_x}
      & $\numeric(@x)$, $\ecalldiff{@x}$
      & The values in $@x$ are a permutation of the numbers $1$ through $\plength(@x)$.
      \\
    \ecprod{v_r}{v_1}{v_2}
      & variables $\{@r, @1, @2\}$ are all $\numeric$ and have the same $\plength$
      & Every element in $@r$ is the product of the corresponding elements in~$@1$ and~$@2$.
      \\
    \ecproj{v_r}{\mathbf{v_x}}
      & $\{@r, @x\}$ all have the same $\plength$, $\por$, $\ptable$ and type; @x contains at least 2~vectors
      & At every position in $1$ through $\plength(@x)$ there is exactly one vector in $@x$ with a non-blank value at that position which is the same as the corresponding value in $@r$.
      \\
    \ecrank{v_r}{v_x}
      & $\integer(@r)$; $\numeric(@x)$; and $\plength(@r) = \plength(@x)$
      & The values in $@r$ represent the rank (from largest to smallest) of the values in ($@x$) - including ties
      \\
    \ectotal{v_r}{v_{pos}}{v_{neg}}
      & $\{@r, @pos, @neg\}$ all have the same $\plength$, which is at least $2$
      & The values in $@r$ are a running total, each value $@r[i] = @r[i - 1] + @pos[i] - @neg[i]$.
      \\
    \ecseries{v_x}
      & $\numeric(@x)$ and $\ecperm{@x}$
      & $@x[1] = 1$ and $@x[i] = @x[i - 1] + 1$.
      \\
    \ecsumc{v_r}{\mathbf{v_x}}
      &
      & Y is the result of summing each column in X \\
    \ecsumr{v_r}{\mathbf{v_x}} & & Y is the result of summing each row in X \\
    \ecsumif{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecsumprod{v_r}{v_1}{v_2} & & \\
